\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
Update src/tex/appendix.tex
Co-authored-by: Martiño Rios-Garcia <147555961+MrtinoRG@users.noreply.github.com>

>>>>

As commented above, \PaperQATwo was outperformed by the \gls{llm} powering it. Similarly, \ClaudeThreeFiveSonnet only slightly improved the results when equipped with some specific tools, while \GPTFourO performance decreased in this same tool environment (see \Cref{sec:react-environment} for further discussion about the ReAct environment). Therefore, a robust chemical agent environment optimized to solve general chemical problems, instead of focusing on bibliographic search or lab work, can be useful in the future.
